Structuring College Access: The Market Segment Model and College Board Geomarkets

### 2025-07-11 text/manuscript-full-KS.qmd
copy edits

*The Structure of College Choice* [@RN4982] created "Geomarkets" and the "Market Segment Mode" (MSM). Geomarkets carve states and metropolitan areas into smaller geographic units to define local recruiting markets. MSM predicts how student demand for a college varies by Geomarket, based on household socioeconomic characteristics. Geomarkets became an input for two College Board recruiting products. First, the Enrollment Planning Service informs which Geomarkets and high schools a college recruits from. Second, the Student Search Service sells prospective student contact information -- or "student lists" -- which colleges filter by Geomarket to determine which prospect profiles to purchase. Drawing from scholarship on quantification, particularly discussions of correlation and homophily, we conceptualize how recruiting products incorporate Geomarkets. We address two research questions: What is the socioeconomic and racial variation between Geomarkets? How does the socioeconomic and racial composition of included versus excluded prospects vary when student lists filter on Geomarkets? We answer RQ1 by analyzing Census data from 1980, 2000, and 2020. RQ2 analyzes data on student lists purchased by public universities, collected through public records requests. Using a quantitative case study design with metropolitan areas as cases, descriptive statistics and interactive maps suggest Geomarkets mirror deeply-rooted patterns of racial and class segregation. Moreover, student lists that exclude low-income Geomarkets systematically overlook non-white students, first-generation students, and especially first-generation non-white students.

@@

On January 9, 2019 a public research university purchased College Board *Student Search Service* order no. $448922$, thereby obtaining the contact information of out-of-state prospective students, who would subsequently receive brochures, postcards, emails, and targeted social media. This was a large student list purchase, yielding $122,426$ "names." At $\$0.45$ per name, the order cost $\$55,091.70$. The order specified three "search filters" to control which names were purchased: first, the 2020 high school graduating class; second, under the heading "College Board Exams," PSAT score range of 1070 - 1180; and third, under the heading "Geography", the order filtered on 67 "Geomarkets," identified by titles like "IL08 - Northwest Suburbs" and "IL09 - North Shore."[^1] The Geomarket filter carves states and metropolitan areas into smaller geographic units. Upon closer inspection, this student list purchase selected all Geomarkets in the Chicago-land area except for "IL10 - City of Chicago," which is significantly poorer and has a higher share of Black residents. Similarly, in the DC/Maryland/Virginia metro area, the order selected the affluent "MD02 - Montgomery Metropolitan," "MD03 - Central Maryland (w/o Baltimore)," "VA01 - Arlington & Alexandria," and "VA02 - Fairfax County" Geomarkets, but excluded the "MD05 - Prince Georges Metropolitan," "MD07 - Baltimore (Urban)," and "DC01 - District of Columbia" Geomarkets.

@@

In 1978, set against the backdrop of impending college-age demographic decline, University of Pennsylvania professor Robert Zemsky, was tasked by the President to figure out, "'Who thinks about Penn?'" and "'What other institutions do they think about when they think about us?" [@RN4982, p. x]. To answer these questions, Zemsky began working with the Market Research Committee of the Consortium on Financing Higher Education (COFHE), a consortium of 30 selective private universities founded in the mid-1970s. The project goal became the creation of the Market Segment Model, which had the lofty ambition of predicting student demand for any college from any locality. However, "to gain a truly comprehensive view of the collegiate enrollment market, we needed a database that described most institutions and most students" [@RN4982, p. x]. The group approached College Board. "Coincidentally, the Board was reviewing its own efforts to help colleges estimate their enrollment potential" [@RN4982, p. x]. Although the analyses of @RN4982 are based on the score-sending behavior of SAT test-takers, the authors had great respect for admissions officers and conceived of the project as an effort to "capture and quantify" (p. 11) their knowledge:

@@

> In many cases, the market boundaries match formal political and educational divisions, reflecting natural channels of communication. Each major metropolitan area is composed of several markets, usually corresponding to the inner city, a first ring of suburbs, and an outer ring of suburbs. In more sparsely populated areas, communities are sometimes combined in order to make the analysis meaningful."

@@

```{=html}
<!-- SAT test-takers were categorized into one of four different market segments -- local, in-state, regional, and national -- based on SAT score-sending behavior. For a given student, each college that receives a score from the student can be defined as "local" (college located in the the same Geomarket as the student), "in-state" (same state but different Geomarket), "regional" (same region but different state), or "national" (different region). In turn, a test-taker is categorized in the "local" market segment if they submit more SAT scores to local institutions than they do to in-state, regional, or national institutions. An "in-state" student submits more SAT scores to in-state institutions than they do to local, regional, or national institutions, etc. 
A "regional" student submits more SAT scores to regional institutions than they do to local, in-state, or national institutions. A "national" student submits more SAT scores to national institutions than they do to local, in-state, or regional institutions.
-->
```
The two primary outputs of the Market Segment Model are the (1) Market Segment Profile and (2) the Institutional Profile. Appendix A describes these outputs in more detail \[CRYSTAL\]. Both outputs are created separately for each Geomarket. For each market segment (local, in-state, regional, national), the Market Segment Profile shows the number of students, their average SAT score, the percent aspiring to a BA+, percent with family in come greater than \$35,000, percent with both parents having a BA, etc.[^5] The Institutional Profile shows the number of students who send scores to a particular institution -- separately by market segment -- and which majors these students are interested in. A university could obtain this for their own institution or for a competitor.[^6] Taken together, the Market Segment Profile shows a college which Geomarkets possess attractive student market segments while the Institutional Profile shows the extent to which students in a particular Geomarket are interested in your college or a competitor college. These outputs became the basis for the Enrollment Planning Service (EPS) software.

@@

[^7]: This is a "two-mode" social network in which students (mode 1) send SAT scores -- the network tie -- to colleges (mode 2). The authors turn this into a one-mode college network that defines two institutions as being in competition with one another -- the network tie -- if at least 15% of students who sent SAT scores to one institution also sent scores to the other institution and vice-versa. Next, the authors develop "tinker toy" diagrams that show which institutions are connected to one another. These diagrams are drawn separately for each student segment -- local, in-state, regional, and national -- and separately for each Geomarket, such that the analyses convey which institutions compete with one another for which student segments in each local market. For example, describing the Figure 4.4 "Structure of Fairfield County Regional Market," [@RN4982, p. 54] state that "competitive overlap, moreover, is often confined to institutions belonging to the same \[Carnegie\] type as well sector. For example, public flagships compete primarily with other public flagships; private standard colleges, with other private standard colleges; Catholic institutions, with other Catholic institutions."

@@

Software documentation by @RN5017 states that "EPS market codes are proprietary market codes owned by the College Board and are used to categorize external organizations and people into geographical areas, mostly in the United States. Some admissions offices use EPS market codes to focus their recruiting efforts in geographic areas in which they believe they will be the most successful."
-->
```
Whereas @RN4982 identified 143 Geomarkets covering the New England, Middle States, and South region, EPS created Geomarkets for the remaining U.S. states, with 304 Geomarkets in total. @RN4988 shows the contemporary Geomarkets. Documentation and promotional material suggests that geomarket borders were chosen based on a combination of formal geographic borders (e.g., counties) as well as proprietary College Board data designed to identify geographic areas with different college-going behaviors.[^8] However, Geomarkets for New England, Middle States, and the South are identical to those developed by @RN4982.

@@

Quantification "disciplines" [@RN5007] actors to react in particular ways. EPS software may discipline colleges to approach recruiting in a manner consistent with the Market Segment Model. Drawing from promotional literature [e.g., @RN5019; @RN1621], @RN4980, and background conversations with enrollment managers, the practical purpose of EPS was to inform the "travel schedule" of admissions recruiters. EPS promotional material and user guides encourages users to begin by identifying which Geomarkets they will recruit from.[^9] Second, EPS users decide which high schools they will visit within selected Geomarkets. Based on the principle of homophily, the Market Segment Model suggests that selective colleges should target Geomarkets with large numbers of affluent, college educated households, while low-income communities are left to local four-year and community colleges. Anecdotally, the salience of Geomarkets and EPS software affected the decision-making authority of admissions officers and the territories that admissions officers were assigned to.[^10] <!-- uc san diego appears to use geomarkets to organize high school visits: inspect the html in this page https://beatriton.ucsd.edu/register/requestschoolvisit -->

@@

[^10]: Quantification often reduces the decision-making authority of local actors [@RN5007]. The Market Segment Model sought to replicate the aggregate knowledge of local admissions officers. Once this knowledge was quantified and commodified onto a CD-ROM, the local expertise of admissions officers becomes less valuable. The EPS product increases the ability of a college admissions leader -- working with College Board staff or an EM consultant -- to plan recruiting efforts centrally. In background conversations, EM professionals told us that EPS software enabled colleges to plan travel without relying on admissions officers having strong local knowledge of their territories. However, EPS software often recommended visiting the same sets of affluent, high-achieving high schools that were receiving visits from other colleges. We were told that savvier, quantitatively-adept admissions offices used EPS to visit schools that EPS recommended ignoring because there would be less competition for the good students who attended these high schools. Finally, Geomarkets were created to mirror the territories of admissions officers [@RN4982]. In turn, as Geomarkets became more salient, admissions offices often structured their territories around Geomarkets. On background, admissions officers and enrollment consultants told us it remains common parlance to hear an admissions officer say something like, "I recruit 'PA 2'," which refers to the "Chester County, PA Geomarket. In states a college recruits heavily from, admissions officers are often assigned specific Geomarkets as their territory. This can be seen in the Chicago-land recruiting territories of University of Chicago \[ADD TO APPENDIX\], of Lake Forest College, of Saint Mary's College \[ADD TO APPENDIX CRYSTAL\]

Because Geomarkets are foundational to EPS software, our first research question is interested in the extent to which this geographical building block is associated with race and class. We ask (RQ1), what is the socioeconomic and racial variation between Geomarkets and how does this variation change over time? @RN4982 viewed demand for higher education as a function of class. They developed 142 Geomarkets borders with an eye towards identifying geographic areas that differed from one another in terms of class composition, while [@RN5016] created the remaining Geomarket borders with an eye towards distinguishing geographies based on college-going behaviors. Considering the extent of class-based residential segregation in the U.S. [@reardon2011], we expect substantial socioeconomic inequality between Geomarkets in large metropolitan areas.

@@

However, @RN5012 argue that student list products may exacerbate racial inequality in college access. The authors conceptualize student list products as "selection devices" [@RN4778] that enable colleges to select which prospective students they target by incorporating search filters (e.g., high school graduating class, state). @RN4786 defines "racialized inputs" as ostensibly race-neutral inputs that are systematically correlated with race because marginalized racial/ethnic groups have historically been excluded from the input [@RN4786]. @RN5012 argue that several frequently utilized student list filters (e.g., zip code, AP test score, SAT score) meet the criteria of racialized inputs. Using a national sample of high school students and using data from actual student lists purchased by public universities, @RN5012 show that racialized search filters have a strong negative relationship with the selection of Black and Latinx prospects.

Because of the extent of residential segregation in the U.S., geographic borders are a commonly studied racialized input in scholarship about algorithmic bias [@RN4775; @RN4849; @RN4887]. Student list products offer many geographic filters. Some geographic filters are based on known geographic borders (e.g., zip code, county, CBSA, state). College Board also created geographic borders that subsequently became filters in the *Student Search Service*, such as Geomarkets and Geodemographic Segment filters.[^14] In their sample, @RN5012 found that 11% of student lists purchased by public research universities filtered on Geomarkets. Drawing from @RN4786, we argue that geomarkets satisfy the two criteria of racialized inputs. First, they are ostensibly race-neutral inputs in that neither @RN4982 -- nor subsequent EPS promotional material [e.g., @RN1621] -- mention race. Second, Geomarkets may be systematically correlated with race. For example, Geomarket "CA07" is "City of Oakland" and "CA08" is "Alameda Country, excluding Oakland." <!--# A university might purchase prospect contact information by filtering on CA08 in combination with additional filters, such as year of high school graduation and SAT test score.--> We extend @RN5012 by examining how the racial composition of actual student list purchases changes if universities filter on particular Geomarkets. <!--# This manuscript focuses on Geomarkets. -->

[^14]: Geodemographic segment filters utilize cluster analysis to allocate each census tract and each high school into different categories based past college enrollment and other factors [@RN4565].

@@

> Imagine that you recruit for a college that draws most of its students from regional or national segments. Where would you concentrate your energies? Ideally, you would seek communities \[Geomarkets\] with a high proportion of students already predisposed toward institutions such as your own. The Market Segment Model would provide this information through segment percentages for the community in question. Further classification of students by social attributes allows you to identify a group for mailings or recruiting\ldots If you were to recruit in Boston, only about two out of every ten students with fewer than two attributes would likely listen \ldots Your efforts would surely be better directed toward \ldots Manchester, Hartford, and Fairfield County \ldots Indeed, in Fairfield County alone you could reach more than 40 percent of your "primary target" population. <!-- -- that is, students with a greater than 75-percent probability of concentrating their college choices among institutions like your own. -->

@@

# Appendix

>>>>

*The Structure of College Choice* [@RN4982] created "Geomarkets" and the "Market Segment Model" (MSM). Geomarkets carve states and metropolitan areas into smaller geographic units to define local recruiting markets. MSM predicts how student demand for a college varies by Geomarket, based on household socioeconomic characteristics. Geomarkets became an input for two College Board recruiting products. First, the Enrollment Planning Service informs which Geomarkets and high schools a college recruits from. Second, the Student Search Service sells prospective student contact information -- or "student lists" -- which colleges filter by Geomarket to determine which prospect profiles to purchase. Drawing from scholarship on quantification, particularly discussions of correlation and homophily, we conceptualize how recruiting products incorporate Geomarkets. We address two research questions: What is the socioeconomic and racial variation between Geomarkets? How does the socioeconomic and racial composition of included versus excluded prospects vary when student lists filter on Geomarkets? We answer RQ1 by analyzing Census data from 1980, 2000, and 2020. RQ2 analyzes data on student lists purchased by public universities, collected through public records requests. Using a quantitative case study design with metropolitan areas as cases, descriptive statistics and interactive maps suggest Geomarkets mirror deeply-rooted patterns of racial and class segregation. Moreover, student lists that exclude low-income Geomarkets systematically overlook non-White students, first-generation students, and especially first-generation non-White students.

@@

On January 9, 2019 a public research university purchased College Board Student Search Service order no. $448922$, thereby obtaining the contact information of out-of-state prospective students, who would subsequently receive brochures, postcards, emails, and targeted social media. This was a large student list purchase, yielding $122,426$ "names." At $\$0.45$ per name, the order cost $\$55,091.70$. The order specified three "search filters" to control which names were purchased: first, the 2020 high school graduating class; second, under the heading "College Board Exams," PSAT score range of 1070 - 1180; and third, under the heading "Geography", the order filtered on 67 "Geomarkets," identified by titles like "IL08 - Northwest Suburbs" and "IL09 - North Shore."[^1] The Geomarket filter carves states and metropolitan areas into smaller geographic units. Upon closer inspection, this student list purchase selected all Geomarkets in the Chicago-land area except for "IL10 - City of Chicago," which is significantly poorer and has a higher share of Black residents. Similarly, in the DC/Maryland/Virginia metro area, the order selected the affluent "MD02 - Montgomery Metropolitan," "MD03 - Central Maryland (w/o Baltimore)," "VA01 - Arlington & Alexandria," and "VA02 - Fairfax County" Geomarkets, but excluded the "MD05 - Prince Georges Metropolitan," "MD07 - Baltimore (Urban)," and "DC01 - District of Columbia" Geomarkets.

@@

In 1978, set against the backdrop of impending college-age demographic decline, University of Pennsylvania professor Robert Zemsky was tasked by the President to figure out, "'Who thinks about Penn?'" and "'What other institutions do they think about when they think about us?'" [@RN4982, p. x]. To answer these questions, Zemsky began working with the Market Research Committee of the Consortium on Financing Higher Education (COFHE), a consortium of 30 selective private universities founded in the mid-1970s. The project goal became the creation of the Market Segment Model, which had the lofty ambition of predicting student demand for any college from any locality. However, "to gain a truly comprehensive view of the collegiate enrollment market, we needed a database that described most institutions and most students" [@RN4982, p. x]. The group approached College Board. "Coincidentally, the Board was reviewing its own efforts to help colleges estimate their enrollment potential" [@RN4982, p. x]. Although the analyses of @RN4982 are based on the score-sending behavior of SAT test-takers, the authors had great respect for admissions officers and conceived of the project as an effort to "capture and quantify" (p. 11) their knowledge:

@@

> In many cases, the market boundaries match formal political and educational divisions, reflecting natural channels of communication. Each major metropolitan area is composed of several markets, usually corresponding to the inner city, a first ring of suburbs, and an outer ring of suburbs. In more sparsely populated areas, communities are sometimes combined in order to make the analysis meaningful.

@@

```{=html}
<!-- SAT test-takers were categorized into one of four different market segments -- local, in-state, regional, and national -- based on SAT score-sending behavior. For a given student, each college that receives a score from the student can be defined as "local" (college located in the the same Geomarket as the student), "in-state" (same state but different Geomarket), "regional" (same region but different state), or "national" (different region). In turn, a test-taker is categorized in the "local" market segment if they submit more SAT scores to local institutions than they do to in-state, regional, or national institutions. An "in-state" student submits more SAT scores to in-state institutions than they do to local, regional, or national institutions, etc. 
A "regional" student submits more SAT scores to regional institutions than they do to local, in-state, or national institutions. A "national" student submits more SAT scores to national institutions than they do to local, in-state, or regional institutions.
-->
```
The two primary outputs of the Market Segment Model are the (1) Market Segment Profile and (2) the Institutional Profile. Appendix A describes these outputs in more detail. Both outputs are created separately for each Geomarket. For each market segment (local, in-state, regional, national), the Market Segment Profile shows the number of students, their average SAT score, the percent aspiring to a BA+, percent with family income greater than \$35,000, percent with both parents having a BA, etc.[^5] The Institutional Profile shows the number of students who send scores to a particular institution -- separately by market segment -- and which majors these students are interested in. A university could obtain this for their own institution or for a competitor.[^6] Taken together, the Market Segment Profile shows a college which Geomarkets possess attractive student market segments while the Institutional Profile shows the extent to which students in a particular Geomarket are interested in your college or a competitor college. These outputs became the basis for the Enrollment Planning Service (EPS) software.

@@

[^7]: This is a "two-mode" social network in which students (mode 1) send SAT scores -- the network tie -- to colleges (mode 2). The authors turn this into a one-mode college network that defines two institutions as being in competition with one another -- the network tie -- if at least 15% of students who sent SAT scores to one institution also sent scores to the other institution and vice-versa. Next, the authors develop "tinker toy" diagrams that show which institutions are connected to one another. These diagrams are drawn separately for each student segment -- local, in-state, regional, and national -- and separately for each Geomarket, such that the analyses convey which institutions compete with one another for which student segments in each local market. For example, describing the Figure 4.4 "Structure of Fairfield County Regional Market," @RN4982 [p. 54] state that "competitive overlap, moreover, is often confined to institutions belonging to the same \[Carnegie\] type as well sector. For example, public flagships compete primarily with other public flagships; private standard colleges, with other private standard colleges; Catholic institutions, with other Catholic institutions."

@@

Software documentation by @RN5017 states that "EPS market codes are proprietary market codes owned by the College Board and are used to categorize external organizations and people into geographical areas, mostly in the United States. Some admissions offices use EPS market codes to focus their recruiting efforts in geographic areas in which they believe they will be the most successful."
-->
```
Whereas @RN4982 identified 143 Geomarkets covering the New England, Middle States, and South region, EPS created Geomarkets for the remaining U.S. states, with 304 Geomarkets in total. @RN4988 shows the contemporary Geomarkets. Documentation and promotional material suggest that geomarket borders were chosen based on a combination of formal geographic borders (e.g., counties) as well as proprietary College Board data designed to identify geographic areas with different college-going behaviors.[^8] However, Geomarkets for New England, Middle States, and the South are identical to those developed by @RN4982.

@@

Quantification "disciplines" [@RN5007] actors to react in particular ways. EPS software may discipline colleges to approach recruiting in a manner consistent with the Market Segment Model. Drawing from promotional literature [e.g., @RN5019; @RN1621], @RN4980, and background conversations with enrollment managers, the practical purpose of EPS was to inform the "travel schedule" of admissions recruiters. EPS promotional material and user guides encourage users to begin by identifying which Geomarkets they will recruit from.[^9] Second, EPS users decide which high schools they will visit within selected Geomarkets. Based on the principle of homophily, the Market Segment Model suggests that selective colleges should target Geomarkets with large numbers of affluent, college-educated households, while low-income communities are left to local four-year and community colleges. Anecdotally, the salience of Geomarkets and EPS software affected the decision-making authority of admissions officers and the territories that admissions officers were assigned to.[^10] <!-- uc san diego appears to use geomarkets to organize high school visits: inspect the html in this page https://beatriton.ucsd.edu/register/requestschoolvisit -->

@@

[^10]: Quantification often reduces the decision-making authority of local actors [@RN5007]. The Market Segment Model sought to replicate the aggregate knowledge of local admissions officers. Once this knowledge was quantified and commodified onto a CD-ROM, the local expertise of admissions officers becomes less valuable. The EPS product increases the ability of a college admissions leader -- working with College Board staff or an EM consultant -- to plan recruiting efforts centrally. In background conversations, EM professionals told us that EPS software enabled colleges to plan travel without relying on admissions officers having strong local knowledge of their territories. However, EPS software often recommended visiting the same sets of affluent, high-achieving high schools that were receiving visits from other colleges. We were told that savvier, quantitatively-adept admissions offices used EPS to visit schools that EPS recommended ignoring because there would be less competition for the good students who attended these high schools. Finally, Geomarkets were created to mirror the territories of admissions officers [@RN4982]. In turn, as Geomarkets became more salient, admissions offices often structured their territories around Geomarkets. On background, admissions officers and enrollment consultants told us it remains common parlance to hear an admissions officer say something like, "I recruit 'PA 2'," which refers to the "Chester County, PA Geomarket." In states a college recruits heavily from, admissions officers are often assigned specific Geomarkets as their territory. This can be seen in the Chicago-land recruiting territories of University of Chicago \[ADD TO APPENDIX\], of Lake Forest College, of Saint Mary's College \[ADD TO APPENDIX CRYSTAL\]

Because Geomarkets are foundational to EPS software, our first research question is interested in the extent to which this geographical building block is associated with race and class. We ask (RQ1), what is the socioeconomic and racial variation between Geomarkets and how does this variation change over time? @RN4982 viewed demand for higher education as a function of class. They developed 143 Geomarkets borders with an eye towards identifying geographic areas that differed from one another in terms of class composition, while [@RN5016] created the remaining Geomarket borders with an eye towards distinguishing geographies based on college-going behaviors. Considering the extent of class-based residential segregation in the U.S. [@reardon2011], we expect substantial socioeconomic inequality between Geomarkets in large metropolitan areas.

@@

However, @RN5012 argue that student list products may exacerbate racial inequality in college access. The authors conceptualize student list products as "selection devices" [@RN4778] that enable colleges to select which prospective students they target by incorporating search filters (e.g., high school graduating class, state). @RN4786 defines "racialized inputs" as ostensibly race-neutral inputs that are systematically correlated with race because marginalized racial/ethnic groups have historically been excluded from the input. @RN5012 argue that several frequently utilized student list filters (e.g., zip code, AP test score, SAT score) meet the criteria of racialized inputs. Using a national sample of high school students and using data from actual student lists purchased by public universities, @RN5012 show that racialized search filters have a strong negative relationship with the selection of Black and Latinx prospects.

Because of the extent of residential segregation in the U.S., geographic borders are a commonly studied racialized input in scholarship about algorithmic bias [@RN4775; @RN4849; @RN4887]. Student list products offer many geographic filters. Some geographic filters are based on known geographic borders (e.g., zip code, county, CBSA, state). College Board also created geographic borders that subsequently became filters in the Student Search Service, such as Geomarkets and Geodemographic Segment filters.[^14] In their sample, @RN5012 found that 11% of student lists purchased by public research universities filtered on Geomarkets. Drawing from @RN4786, we argue that geomarkets satisfy the two criteria of racialized inputs. First, they are ostensibly race-neutral inputs in that neither @RN4982 -- nor subsequent EPS promotional material [e.g., @RN1621] -- mention race. Second, Geomarkets may be systematically correlated with race. For example, Geomarket "CA07" is "City of Oakland" and "CA08" is "Alameda County, excluding Oakland." <!--# A university might purchase prospect contact information by filtering on CA08 in combination with additional filters, such as year of high school graduation and SAT test score.--> We extend @RN5012 by examining how the racial composition of actual student list purchases changes if universities filter on particular Geomarkets. <!--# This manuscript focuses on Geomarkets. -->

[^14]: Geodemographic segment filters utilize cluster analysis to allocate each census tract and each high school into different categories based on past college enrollment and other factors [@RN4565].

@@

> Imagine that you recruit for a college that draws most of its students from regional or national segments. Where would you concentrate your energies? Ideally, you would seek communities \[Geomarkets\] with a high proportion of students already predisposed toward institutions such as your own. The Market Segment Model would provide this information through segment percentages for the community in question. Further classification of students by social attributes allows you to identify a group for mailings or recruiting\ldots If you were to recruit in Boston, only about two out of every ten students with fewer than two attributes would likely listen\ldots Your efforts would surely be better directed toward\ldots Manchester, Hartford, and Fairfield County\ldots Indeed, in Fairfield County alone you could reach more than 40 percent of your "primary target" population. <!-- -- that is, students with a greater than 75-percent probability of concentrating their college choices among institutions like your own. -->

@@

# Appendix A
